True versus apparent shapes of astrophysical bow shocks

### 2016-03-03 papers/Paper1/sec-application.tex
Inserting new figures in article

Expanding (\ref{eq:th190}) until 3rd order and solving for $\theta_{1,90}$:
\begin{align}
\theta_{1,90} \simeq \left(\frac{2.4\beta}{1-0.8\beta}\right)^{1/2} \\
R_{90} \simeq \left(\frac{2.4\beta}{(1-0.8\beta)^3}\right)^{1/2}
\label{eq:r90}
\end{align}
%%%% Here we go in edition

@@

\subsubsection{Metodology}
Using the DS9 SAO image tools, we marked the positions of the proplyds and $\theta_1^C$. We followed the brightness contours along the 
bow shocks to mark the shell's position. In order to obtain the set of measurements $(R_0, R_c, D)$, we moved to the proplyd's reference frame, (where the proplyd's position)
is $(0,0)$ and measured distances in arcseconds. In this reference, the proplyd-$\theta_1^C$ line is $y=0$. With the shell's positions, we optimize a circle, whose radius is $R_c$, but
this optimization has two variants: the first one with the restriction that the center of the circle must lie in the symmetry axis (y=0), and the second variation is with no restrictions. The figure (\ref{fig:radii-measures-example}) shows a representation of the metodology described. 
Our first goal was comparing measurements of $(R_0,R_{90})$ of the LV group of proplyds in mid infrared by \citep{Robberto:2005} against observations in [OIII] with better angular resolution but less contrast against
the background.
In \citep{Robberto:2005} they compare their observations with shells obtained with the \citep{Canto:1996} two winds interactions formalism. They found no concordance between the model and observations. We attempted to redo the measurements with better resolution observations. We found quickly that we cannot measure $R_{90}$ in a reliable way since the shell's brightness decays toward the wings. Also, we are using a more sophisticated model where the proplyd's wind density decays as $n \propto \cos {1/2}\theta$ instead of an isotropic wind.
A better replacement of $R_{90}$ is the radius of curvature, defined as the radius of the circle that fits the observations, because always is measurable. Figures (\ref{fig:char-radii-obs}) and (\ref{fig:char-radii-obs-2}) show our measurements of the radius of curvature for the LV group, with exception of LV1, which actually is a binary proplyd, thus our model is not adequate in this case. Also we include the proplyds 167-328 and 177-341 (HST1) which are close enough to $\theta^1~\mathrm{C~Ori}$ to be influenced by it stellar wind.
Our results show a better concordance (but still not perfect) between models and observations, as shown in figure (\ref{fig:prop-shell-err}). A possible cause of the discrepancy may be that the \citep{Canto:1996} model assumes that the interacting winds are hypersonic in such way that the shocked gas can be considered as a bidimensional surface. In practice, the bow shock has a finite width, which can afect the apparent shape due to projection effects

\begin{figure*}
\begin{tabular}{cc}
\includegraphics[width=0.45\linewidth]{proplyd-shell-R0-Rc-errors-1} &
\includegraphics[width=0.45\linewidth]{proplyd-shell-R0-Rc-new}
\end{tabular}
\label{fig:prop-shell-err}
\caption{Measurements of proplyd's characteristic radii $R_c$ and $R_0$. The curves represent a single bow shock with  fixed wind's momentum ratio $\beta$. The dots represent separations in inclination of $15^{\circ}$. The semitransparent curves represent bow shocks which the inner wind is isotropic and the full colored curves bow shocks which inner wind density decays as $\cos^{1/2}\theta$. Our measures match far better than \citep{Robberto:2005}, but our data tend to lie at high inclinations $i \gtrsim 45^\circ$, when we expected the opposite. Right side: The same}
\end{figure*}
%Initially we tried to measure the radii $(R_0,R_{90})$, but it wasn't possible due to the fact that the brightness of the shell decays rapidly towards the wings, and using $R_\theta$ where $60 \lesssim \theta < 0 $ is not so useful, because there is not a significant difference between $R_0$ and $R_\theta$. Instead, we introduced the radius of curvature after we realized how well the shell's marks fits into a circle for all the proplyds (see figure (\ref{fig:char-radii-obs})).

@@

>>>>

Expanding (\ref{eq:th190}) until 3rd order and solving for $\theta_{1,90}$:
\begin{align}
\theta_{1,90} \simeq \left(\frac{2.4\beta}{1-0.8\beta}\right)^{1/2} \\
R_{90} \simeq \left(\frac{2.4\beta}{(1-0.8\beta)^3}\right)^{1/2}
\label{eq:r90}
\end{align}

@@

\subsubsection{Metodology}
Using the DS9 SAO image tools, we marked the positions of the proplyds and $\theta_1^C$. We followed the brightness contours along the 
bow shocks to mark the shell's position. In order to obtain the set of measurements $(R_0, R_c, D)$, we moved to the proplyd's reference frame, (where the proplyd's position)
is $(0,0)$ and measured distances in arcseconds. In this reference, the proplyd-$\theta_1^C$ line is $y=0$. With the shell's positions, we optimize a circle, whose radius is $R_c$, but
this optimization has two variants: the first one with the restriction that the center of the circle must lie in the symmetry axis (y=0), and the second variation is with no restrictions. $R_0$ is calculated as the distance between the proplyd position and the bow shock in a line which is also included the
center of curvature. The figure (\ref{fig:radii-measures-example}) shows a representation of the metodology described. 
Our first goal was comparing measurements of $(R_0,R_{90})$ of the LV group of proplyds in mid infrared by \citep{Robberto:2005} against observations in [OIII] with better angular resolution but less contrast against
the background.
In \citep{Robberto:2005} they compare their observations with shells obtained with the \citep{Canto:1996} two winds interactions formalism. They found no concordance between the model and observations. We attempted to redo the measurements with better resolution observations. We found quickly that we cannot measure $R_{90}$ in a reliable way since the shell's brightness decays toward the wings. Also, we are using a more sophisticated model where the proplyd's wind density decays as $n \propto \cos {1/2}\theta$ instead of an isotropic wind.
A better replacement of $R_{90}$ is the radius of curvature, defined as the radius of the circle that fits the observations, because always is measurable. Figures (\ref{fig:char-radii-obs}) and (\ref{fig:char-radii-obs-2}) show our measurements of the radius of curvature for the LV group, with exception of LV1, which actually is a binary proplyd, thus our model is not adequate in this case. Also we include the proplyds 167-328, 169-338, 177-341 (HST1), 189-339 and 180-331 which are close enough to $\theta^1~\mathrm{C~Ori}$ to be influenced by it stellar wind.
Our results show a better concordance (but still not perfect) between models and observations, as shown in figure (\ref{fig:prop-shell-err}). A possible cause of the discrepancy may be that the \citep{Canto:1996} model assumes that the interacting winds are hypersonic in such way that the shocked gas can be considered as a bidimensional surface. In practice, the bow shock has a finite width, which can afect the apparent shape due to projection effects

\begin{figure*}
\begin{tabular}{cc}
\includegraphics[width=0.45\linewidth]{proplyd-shell-R0-Rc-errors-1} &
\includegraphics[width=0.45\linewidth]{proplyd-shell-R0-Rc-errors-new}
\end{tabular}
\label{fig:prop-shell-err}
\caption{Measurements of proplyd's characteristic radii $R_c$ and $R_0$. The curves represent a single bow shock with  fixed wind's momentum ratio $\beta$. The dots represent separations in inclination of $15^{\circ}$. The semitransparent curves represent bow shocks which the inner wind is isotropic and the full colored curves bow shocks which inner wind density decays as $\cos^{1/2}\theta$. Our measures match far better than \citep{Robberto:2005}, but our data tend to lie at high inclinations $i \gtrsim 45^\circ$, when we expected the opposite. Right side: The same}
\end{figure*}
%Initially we tried to measure the radii $(R_0,R_{90})$, but it wasn't possible due to the fact that the brightness of the shell decays rapidly towards the wings, and using $R_\theta$ where $60 \lesssim \theta < 0 $ is not so useful, because there is not a significant difference between $R_0$ and $R_\theta$. Instead, we introduced the radius of curvature after we realized how well the shell's marks fits into a circle for all the proplyds (see figure (\ref{fig:char-radii-obs})).

@@

\begin{figure*}
\begin{tabular}{cc}
\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-OIII3b-169-338} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3b-169-338} \\
\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-OIII3b-189-329} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3b-189-329}\\
\includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-OIII3a-180-331} & \includegraphics[width=0.5\linewidth]{LV-bowshocks-xyfancy-onaxis-OIII3a-180-331}
\end{tabular}
\label{fig:char-radii-obs-3}
\caption{Continuation of figure (\ref{fig:char-radii-obs}), (new sample)}
\end{figure*}
